---
title: "Final Project Proposal"
author: "Enxhi Buxheli"
date: "10/19/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(tidyverse)
library(janitor)
```

### Government Revenue and Spending and its Effect of Quality of Living
I will be looking into data related to government spending and taxation and
its effect on the quality of life for its citizens. The goal is to use global 
and national tax data among other datasets in order to assess this relation.
Something I've noted in my initial search for data is that on a global level
data is sparse in lesser developed countries which might lead to some changes 
in the scope of the project and building visualizations and telling stories 
with the data.

Below is just some code that shows I have loaded some data and have created a 
summary statistic from this data.

```{r}
# loading in World Bank tax data 
# [https://data.worldbank.org/indicator/GC.TAX.TOTL.GD.ZS]

tax_global <- read_csv("global_taxdata.csv", skip = 4) %>% 
  clean_names() %>% 
  select(everything(), -indicator_code, -indicator_name, -x63)

# count of # of countries in dataset
tax_global %>% 
  summarise(n())
```